### 2020-09-28 README.Rmd
Change OSAT link
Change link to CoC and version

- The [OSAT](https://bioconductor.org/packages/OSAT/) package handles categorical 
variables but not numeric data. It doesn't work with our data.

@@

Please note that this project is released with a [Contributor Code of Conduct](https://llrs.github.io/experDesign/CODE_OF_CONDUCT.html).
By participating in this project you agree to abide by its terms.

>>>>

- The [OSAT](https://bioconductor.org/packages/release/bioc/html/OSAT.html) package handles categorical 
variables but not numeric data. It doesn't work with our data.

@@

Please note that this project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/1/0/0/code-of-conduct/).
By participating in this project you agree to abide by its terms.
